Cultural Transmission and Technological Transitions during the Late Paleolithic in Korea

### 2023-02-17 analysis/paper/paper.qmd
Edit text more (methods)

After the first discovery of stemmed points at the Seokjangri site at the 1960s, more than 450 have been found in nearly 30 sites across Korea (@fig-map) [@Sohn_1967; @lee2019were; @Chong_2021]. While most sites contain only a few points, a few sites have many more, such as Suyanggae (n = 55), Jingeuneul (n = 99), and Yongsandong (n = 38) [@Kim_2017]. Among these stemmed points, we selected those that are unbroken from the tip to the stem. We excluded artifacts that were recorded as stemmed points but lack a stem. This resulted in a sample of `r total_number_of_sp` stemmed points from `r total_number_of_assemblages` assemblages unearthed from `r total_number_of_sites` sites spanning the period 40-17 ka (@tbl-sp-number). The images of the stemmed points were obtained through published excavation reports and direct photography during our research in local museums. We defined multiple assemblages from a site where artifact-bearing deposits were separated by culturally sterile deposits, or where distinct artifact-bearing stratigraphic units could be identified by major differences in the texture, color, and composition of the sedimentary deposits.

>>>>

After the first discovery of stemmed points at the Seokjangri site in the 1960s, more than 450 have been found in nearly 30 sites across Korea (@fig-map) [@Sohn_1967; @lee2019were; @Chong_2021]. While most sites contain only a few points, a few sites have many more, such as Suyanggae (n = 55), Jingeuneul (n = 99), and Yongsandong (n = 38) [@Kim_2017]. Among these stemmed points, we selected those that are unbroken from the tip to the stem. We excluded artifacts that were recorded as stemmed points but lack a stem. This resulted in a sample of `r total_number_of_sp` stemmed points from `r total_number_of_assemblages` assemblages unearthed from `r total_number_of_sites` sites spanning the period 40-17 ka (@tbl-sp-number). The images of the stemmed points were obtained through published excavation reports and direct photography during our research in local museums. We defined multiple assemblages from a site where artifact-bearing deposits were separated by culturally sterile deposits, or where distinct artifact-bearing stratigraphic units could be identified by major differences in the texture, color, and composition of the sedimentary deposits.
